### 2019-11-06 report/paper.tex
Describe data used throughout the project (not finished)

>>>>

Across all approaches, we've only been working with the data that was handed to us as part of the assignment. Although our code alters the given data wherever needed, we did neither add any entirely new data from sources like the internet nor did we manually improve the existing data as could be achieved by adding or improving annotations.\\

\begin{itemize}
    \item 80 high resolution images from the \textit{Where's Waldo} book series
    \item 
    \item training a linear support vector machine (SVM) to create a multiclass-classifier
\end{itemize}
